Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-02-02 paper.tex
Fixing my name
some comments about SOM have been fixed and Table3 is changed accordingly

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
\author {
P.A. Castillo$^1$, A.M. Mora$^1$, J.J. Merelo$^1$, H. Fariss$^2$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
}
\institute{
$^1$Department of Computer Architecture and Computer Technology. CITIC. University of Granada (Spain)\\
$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
           e-mail: {\tt pacv@ugr.es}
}

@@

In Figure \ref{fig:Umatrix} we label the U-matrix with the total-sales categories. It can be clearly shown that the SOM algorithm has successfully clustered the labels of the Total Sales into clear identified regions. In the top of the U-matrix the VL category is located. The L category appears in the middle of the matrix. Most of the M category appears in bottom-right corner while the H and VH categories are concentrated in the bottom-left corner. 
Inspecting the component \texttt{distrib\_novelity}, \texttt{tot\_points\_sale}, \texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run} components have the highest similarity to the clusters shown in the U-matrix. Based on this analysis, those features will be selected for the next stage.

@@

\begin{table}
\begin{tabular}[htb]{|c|c|c|c|c|}
\hline
Variable  & PreSales & ReliefFAttributeEval  & SOM & CfsSubsetEval \\ \hline \hline
subject1    & $\checkmark$  &   &   &   \\ \hline
subject2    & $\checkmark$  &   &   &   \\ \hline
subject3    & $\checkmark$  &   &   &   \\ \hline
editorial   & $\checkmark$  &   &   &   \\ \hline
collection  & $\checkmark$  &   &   &   \\ \hline
binding   & $\checkmark$  &   &   &   \\ \hline
ret\_pricer    & $\checkmark$  &   & $\checkmark$  &   \\ \hline
reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  &   \\ \hline
num\_reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
gifts   & $\checkmark$  &   & $\checkmark$  &   \\ \hline
distrib\_novelty   & $\checkmark$  & $\checkmark$  & $\checkmark$  &   \\ \hline
tot\_points\_sale   & $\checkmark$  & $\checkmark$  &   & $\checkmark$  \\ \hline
tot\_points\_sale\_1st\_year    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
weeks\_sale    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
print\_run   & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
total\_sales   & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline

>>>>

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
\author {
P.A. Castillo$^1$, A.M. Mora$^1$, J.J. Merelo$^1$, H. Faris$^2$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
}
\institute{
$^1$Department of Computer Architecture and Computer Technology. CITIC. University of Granada (Spain)\\
$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
           e-mail: {\tt pacv@ugr.es}
}

@@

In Figure \ref{fig:Umatrix} we label the U-matrix with the total-sales categories. It can be clearly shown that the SOM algorithm has successfully clustered the labels of the Total Sales into clear identified regions. In the top of the U-matrix the VL category is located. The L category appears in the middle of the matrix. Most of the M category appears in bottom-right corner while the H and VH categories are concentrated in the bottom-left corner. 
By inspecting \texttt{num\_novility}, \texttt{gifts}, \texttt{distrib\_novelity}, \texttt{tot\_points\_sale}, \texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run} components, it can be noticed that they have the highest similarity to the clusters shown in the U-matrix. Based on this analysis, those features will be selected for the next stage.

@@

\begin{table}
\begin{tabular}[htb]{|c|c|c|c|c|}
\hline
Variable  & PreSales & ReliefFAttributeEval  & SOM & CfsSubsetEval \\ \hline \hline
subject1    & $\checkmark$  &   &   &   \\ \hline
subject2    & $\checkmark$  &   &   &   \\ \hline
subject3    & $\checkmark$  &   &   &   \\ \hline
editorial   & $\checkmark$  &   &   &   \\ \hline
collection  & $\checkmark$  &   &   &   \\ \hline
binding   & $\checkmark$  &   &   &   \\ \hline
ret\_pricer    & $\checkmark$  &   &   &   \\ \hline
reprints    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
num\_reprints    & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
gifts   & $\checkmark$  &   & $\checkmark$  &   \\ \hline
distrib\_novelty   & $\checkmark$  & $\checkmark$  & $\checkmark$  &   \\ \hline
tot\_points\_sale   & $\checkmark$  & $\checkmark$  & $\checkmark$   & $\checkmark$  \\ \hline
tot\_points\_sale\_1st\_year    & $\checkmark$  & $\checkmark$  &  $\checkmark$ &   \\ \hline
weeks\_sale    & $\checkmark$  & $\checkmark$  &   &   \\ \hline
print\_run   & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
total\_sales   & $\checkmark$  & $\checkmark$  & $\checkmark$  & $\checkmark$  \\ \hline
